---
title: "Assignment 2-B"
author: "PLSC 21510/31510"
date: "Fall 2022"
output: pdf_document
---

### Instructions

- __Assigned__: Apr 7
- __Due__: Apr 15

Answer the questions below. Knit this `.Rmd` document as a pdf and submit the pdf file in Canvas. Please avoid printing long outputs (like entire dataframes). 

```{r message = FALSE}
library(tidyverse)
library(rvest)
library(stringr)
library(purrr)
library(lubridate)
library(rtweet)
```

## Part 1: Webscraping

This [page](https://www.ilga.gov/senate/default.asp?GA=98) contains a list of Illinois State Senators. For each senator, the `bills` link points to a list of bills that senator sponsored. From there, you can see the bills where the senator was a *Primary Sponsor*. For example, this [page](https://www.ilga.gov/senate/SenatorBills.asp?GA=98&MemberID=1911&Primary=True) contains all bills for which Pamela Althoff was a primary sponsor.

Your goal is to create a spreadsheet of bills, including information on each bill as well as each senator. 

The end goal should be a dataset identical to the one I've provided for you in `data/bills.csv`

Split the code up into discrete steps, each with their own corresponding Rmarkdown chunk. Use subheaders as necessary. Document each step in clear but concise Rmarkdown prose.


## Part 2: RTweet

Work through the tutorial `2_Collecting/4_RTweet-Demo.Rmd`, which can be found in the main course materials. Below, enter your answers to the challenges.

#### Challenge 1: Hashtag Challenge.

Using the documentation for `search_tweets` as a guide, try pulling the 2,000 most recent tweets that include `#DukeEllington` OR `"Duke Ellington"` -- be sure to exclude retweets from the query.

1. Why did your query not return 2,000 results?

2. Identify the user that has used either the hashtag or the string in the greatest number of tweets -- where is this user from?

```{r, message=FALSE}
# YOUR CODE HERE
```

#### Challenge 2. 

Pick your favorite musical artist and collect the 1,000 most recent tweets they are mentioned in (either by their handle or plain text). What is the most frequently used hashtag in these tweets other than #artistname? 

**HINT**: To simplify this challenge, exclude Tweets with more than one hashtag using:

```{r eval = F}
## Hint: Filter out tweets with multiple hashtags 
## Don't try to run this code before defining "music_tweets"
music_tweets %>%
 mutate(hashtags = as.character(hashtags)) %>%
 filter(!is.na(hashtags),
        !str_detect(hashtags, "c\\("))
```

```{r}
# YOUR CODE HERE
```


#### Challenge 3.

Run the code below to by pull the 1,000 most recent tweets from 5 UChicago faculty members:

```{r}
profs1000 <- get_timeline(
  user = c("carsonaust", "profpaulpoast", "pstanpolitics", 
           "rochelleterman", "bobbygulotty"),
  n = 1000
)
```

Which professors in the `profs1000` data use their iPhone to tweet? What percentage of their total tweets were sent from their iPhone?

```{r}
# YOUR CODE HERE
```

